---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# coinflip538

The goal of coinflip538 is to solve a 538 puzzle, which goes like this: 

> If you have a fake coin that returns head with probability 0.6 and a fair coin
  which returns head and tail with probability 0.5, how many times to you need 
  to flip the coins to know with 95% certainty which coin is fake?
  
This repo illustrates how to solve this question with base R + tidyverse but
no additional statistical library and in a functional programming style. To 
understand the source code, solve the problem "bottom-up". I.e. look at 
`p_fair()` and `p_fake()` to compute probabilities of fair and fake coins 
with just one flip first. 
Then, conditional independence with `p_prod_fair_fake()`. Next, we put it 
together with summing the probabilities resulting form all combinations up 
(`p_fake_gt_fair()`) and a final function (`p_correctly_identify_coins()`) 
potentially allows for guessing in situations when the heads of both coins
have the same count.

Note that every function is just a few lines long, has consistent naming of 
arguments, variable names, simple input and output.



## Installation

```{r}
library(coinflip538)
data <- tibble::tibble(
  N = 1:150,
  p = purrr::map_dbl(.data$N, p_correctly_identify_coins)
)

ggplot2::ggplot(data, ggplot2::aes(x = N, y = p)) + 
  ggplot2::geom_line()


p_correctly_identify_coins(143, allow_guessing = FALSE)
p_correctly_identify_coins(134)

```

